Current and future constraints on primordial magnetic fields

### 2017-06-13 pmf.tex
edited the tex around eq (3)

We use MCMC methods to determine the parameter constraints reported in this work. 
The results are calculated using  the {\textsc CosmoMC}\footnote{http://cosmologist.info/cosmomc (July 2015 version)} package \citep{lewis02b}. 
CosmoMC invokes  CAMB\footnote{http://camb.info}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
Although CosmoMC and CAMB have a partial implementation of PMFs, we choose to adopt a simpler, fast, template-based calculation for the PMF-sourced power. 
We have adapted CosmoMC to add a scaled version of a PMF template to all four CMB power spectra: TT, TE, EE, and BB, where the scale factor is \apmf. 
\be
\changed{C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]}
\ee
\changed{The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events. }
Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.

@@

As noted in the last section, the MCMC includes a  scaling parameter, \apmf{}, for the PMF power spectrum template. 
We can translate the amplitude constraint on this template to a constraint on the r.m.s. magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
\be \label{eqn:scaling}
\apmf \propto \bpmf^4.
\ee
An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed power lead to only modestly better limits on the magnetic field strength. 
However, if a PMF is detected, the steep scaling between \bpmf{} and the observed CMB B-mode power spectrum would allow excellent constraints on the PMF properties.

\changed{The power in the tensor modes also depends on the timing of PMF generation relative to neutrino decoupling. 
We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as:
\be \label{eqn:betascaling}
\apmf^{tens} \propto \beta^{1.9},
\ee
to an excellent approximation. 
We use this $\beta$ power law form to handle the PMF timing dependence. }

>>>>

We use MCMC methods to determine the parameter constraints reported in this work. 
The results are calculated using  the {\textsc CosmoMC}\footnote{http://cosmologist.info/cosmomc (July 2015 version)} package \citep{lewis02b}. 
CosmoMC invokes  CAMB\footnote{http://camb.info}  \citep{lewis00} to calculate the CMB power spectrum for each set of cosmological parameters. 
Although CosmoMC and CAMB have a partial implementation of PMFs, we choose to adopt a simpler, fast, template-based calculation for the PMF-sourced power. 
We have adapted CosmoMC to add a scaled version of a PMF template to all four CMB power spectra: TT, TE, EE, and BB, where the scale factor is \apmf. 
\be
\changed{C_\ell = C_\ell^{\rm{CAMB}} + \apmf \left[\cpmfvec + \left(\frac{\beta}{20}\right)^{1.9}  \cpmftens \right]}\label{clmodel}
\ee
\changed{The calculation of the PMF templates, \cpmfvec{} and \cpmfvec{}, and the motivation for the $\beta$ scaling are described in \S\ref{sec:template}. 
The parameter $\beta = {\rm ln}(a_{\nu}/a_{\rm{PMF}})$ relates the timing of neutrino decoupling and the generation of the PMF, where $a_x$ represents the scale factor at the respective events. }
Note that no other effect of  PMFs is considered; this is one reason we only use CMB data.

@@

As noted in the last section, the MCMC includes a  scaling parameter, \apmf{}, for the PMF power spectrum template. 
We can translate the amplitude constraint on this template to a constraint on the r.m.s. magnetic field strength on 1\,Mpc scales, \bpmf, using the expected scaling:
\be \label{eqn:scaling}
C_{\ell}^{\rm{vec}} \propto \bpmf^4.
\ee
An unfortunate consequence of this steep fourth-power scaling is that substantial reductions in the observationally allowed power lead to only modestly better limits on the magnetic field strength. 
However, if a PMF is detected, the steep scaling between \bpmf{} and the observed CMB B-mode power spectrum would allow excellent constraints on the PMF properties.

\changed{The power in the tensor mode depends on the timing of PMF generation relative to neutrino decoupling. 
%We evaluate the tensor power predicted by the \citet{zucca16} code while stepping $\beta$ by two from 2 to 20, and find it scales as $\beta^{1.9}$ to an excellent %approximation. 
We use the code developed by \citet{zucca16} to compute the tensor power spectra with a fixed magnetic field strength but different $\beta$ values. Given the fact that the amplitude of the tensor mode reaches the maximum around $\ell$ = 100, we assume a simple power law and extrapolate the scaling relation between the power and the parameter $\beta$ from an ensemble of amplitudes at $\ell$ =100. Similar to the vector mode, the tensor power depends on the amplitude of the magnetic field as well. 
%We use this $\beta$ power law form to handle the PMF timing dependence. 
Thus the tensor PMF power scales as:
\be \label{eqn:betascaling}
C_{\ell}^{\rm{tens}} \propto  \bpmf^4 \beta^{1.9},
\ee
which corresponds to the last term in Eq. (\ref{clmodel}).
}
